\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-02 paper.tex
sans serif font for ontology excerpts

\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\tt, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=LimeGreen!50}]

@@

\resizebox{0.7\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\tt, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=BurntOrange!50}]

>>>>

\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\sf, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=LimeGreen!50}]

@@

\resizebox{0.7\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\sf, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=BurntOrange!50}]
